---
title: "ArcticHub summer season"
format: html
editor: visual
---

Summer is here -- at least in Aarhus :) -- and the field season is about to take off for many of us! So here's a little overview of where people will be hanging out digging, counting, flying drones and what not over the next couple of months.

I've hidden all the code in a separate script (`2023-06_ArcticHub_fieldwork_map.R`), but you are of course welcome to have a peek and recycle it as it's useful!

```{r setup, include = FALSE}
source("2023-06_ArcticHub_fieldwork_map.R")
```

So where are we all heading?

```{r}
fieldwork_map_places_legend
```

That's a pretty nice longitudinal spread we will have between us, from 
`r paste(coords_add |> slice_max(lat, n = 1) |> pull(lat) |> round(digits = 1)) |> abs()`
째N (
`r paste(coords_add |> slice_max(lat, n = 1) |> mutate(name = name |> str_replace(", ", " and "), place_name = paste(place, name, sep = ", ") |> pull(place_name))`
) to 
`r paste(coords_add |> slice_min(lat, n = 1) |> pull(lat) |> round(digits = 1)) |> abs()`
째S (
`r paste(coords_add |> slice_min(lat, n = 1) |> mutate(name = name |> str_replace(", ", " and "), place_name = paste(place, name, sep = ", ") |> pull(place_name))`
) and from 
`r paste(coords_add |> slice_min(lon, n = 1) |> pull(lon) |> round(digits = 1)) |> abs()`
째W (
`r paste(coords_add |> slice_min(lon, n = 1) |> mutate(name = name |> str_replace(", ", " and "), place_name = paste(place, name, sep = ", ") |> pull(place_name))`
) to 
`r paste(coords_add |> slice_max(lon, n = 1) |> pull(lon) |> round(digits = 1)) |> abs()`
째E (
`r paste(coords_add |> slice_min(lon, n = 1) |> mutate(name = name |> str_replace(", ", " and "), place_name = paste(place, name, sep = ", ") |> pull(place_name))`
). And things will get pretty crowded on the Greenlandic West coast.

Curious where individual people will go? 

```{r}
fieldwork_map_names_legend
```

Jeff wins the prize for northernmost spot (obviously, looking for the *northernmost plant*), and him, Isla and Madi, Wilhelm and Naia and Maj will all have a lot of travelling to do with at least 3 stops on their summer journeys.

And how will individual groups' members be spread out?
```{r}
fieldwork_map_labs_legend
```

Impressive spread in Team Shrub and the EDGE lab! Better keep track of each other's time difference when communicating (:

To wrap it up, just for fun, here's the same plot again, though this time in an interactive format:
```{r}
fieldwork_map_plotly
```

**Safe travels everyone, stay safe and good luck getting all that exciting data in!**